---
title: "Who Am I?"
about:
  template: jolla
execute:
  echo: false
title-block-banner: true
---

I'm Ammar Aldawood, an aspiring computational biologist.
A medical laboratory sciences alumnus from Jordan University
of Science and Technology, I became increasingly aware of how 
indispensible mathematics and computation are for understanding biology.
\
\

---

## Education & Learning

```{r}
library(tidyverse)

df <- data.frame(
  education = c(
    "BSc in Medical\n Laboratory Sciences",
    "MSc in Microbiology\n and Immunology",
    "Mathematics,\nComputation and Omics"
  ),
  start = c("2017-10-15", "2021-10-15", "2022-06-15"),
  end = c("2021-07-21", "2025-10-31", "2025-10-31"),
  mode = c("Formal Education", "Formal Education", "Autodidacticism")
)

df <- df %>%
  mutate(start = as.Date(start), end = as.Date(end))

df_tidy <- df %>%
  gather(key = date_type, value = date, -education, -mode)

ggplot() +
  geom_line(
    data = df_tidy,
    mapping = aes(
      x = fct_rev(fct_inorder(education)),
      y = date,
      color = mode
    ),
    size = 10
  ) +
  coord_flip() +
  labs(x = "", y = "") +
  scale_color_manual(values = c(
    "Formal Education" = "#ffffff",
    "Autodidacticism" = "#ff8c00"
  )
  ) +
  theme(
    legend.title = element_blank(),
    plot.background = element_rect(fill = "transparent", color = NA),
    panel.background = element_rect(fill = "transparent", color = NA),
    legend.background = element_rect(fill = "transparent", color = NA),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),

    text = element_text(color = "white", size = 12),
    axis.text = element_text(color = "white", size = 12),
    axis.title = element_text(color = "white", size = 12),
    plot.title = element_text(color = "white", size = 12),
    legend.text = element_text(color = "white", size = 12)
  )

```

###### Gantt chart generated using ggplot2 in R

---

## My Tech Stack
##### Hover over nodes to see more info!

```{r}
library(plotly)

n1 <- c("Assembly", "C", "C++", "Python", "R")
n2 <- c("Swift", "SQL", "Shell", "Docker", "Git")

c1 <- c("lightgray", "darkorange", "lightgray", "white", "white")
c2 <- c("white", "white", "darkorange", "white", "white")

node_descriptions <- c(
  "Low level programming.\nLearned it purely to become\nmore 
  grounded in computation and\nunderstand 
  the full picture down to hardware.\nSkill level: ★",
  "Mid level programming.\nUseful for optimization 
  and\nhigh performance computing.\nGives 
  the best control over embedded systems.\nSkill level: ★★",
  "Mid level programming.\nA superset of C that is relevant 
  for\ninteroperability with higher level languages.\nSkill level: ★",
  "High level programming.\nGives access to mature machine 
  learning\npackages such as XGBoost & 
  PyTorch.\nContains the package Biopython.\nSkill level: ★★★★",
  "High level programming.\nSpecialized in data visualization 
  and\nstatistical data analysis.\nContains 
  the library Bioconductor.\nSkill level: ★★★★",
  "High level programming.\nNative app development 
  for more than five different platforms\nin 
  iOS, iPadOS, macOS, watchOS, visionOS..etc.\nSkill level: ★★★★",
  "Structured query language.\nEssential for any meaningful 
  work using big data.\nBest way to 
  interact with relational databases.\nSkill level: ★★★",
  "Command line interface.\nProvides broad access over 
  the system you're working on.\nEssential 
  for scripting and SSH-ing.\nSkill level: ★★★★",
  "Containerization and Reproducibility.\nSkill level: ★★",
  "Version Control and Reproducibility.\nSkill level: ★★★★"
)

fig <- plot_ly(
               type = "sankey",
               arrangement = "snap",
               orientation = "v",
               node = list(
                           label = c(n1, n2),
                           color = c(c1, c2),
                           pad = 15,
                           customdata = node_descriptions,
                           hovertemplate = "<b>Node:</b> 
                           %{label}<br><b>Info:</b> 
                           %{customdata}<extra></extra>"),
               link = list(
                           source = c(0, 1, 1, 1, 1, 2, 2, 2, 6, 6, 7, 7),
                           target = c(1, 2, 3, 4, 5, 3, 4, 5, 3, 4, 8, 9),
                           value = c(6, 3, 1, 1, 1, 1, 1, 1, 1, 1, 1, 1),
                           color = c("lightgray", "darkorange", "darkorange",
                                     "darkorange", "darkorange", "lightgray",
                                     "lightgray", "lightgray", "white",
                                     "white", "darkorange", "darkorange"),
                           hoverinfo = "none"))
fig <- fig %>% layout(title = "",
  paper_bgcolor = "rgba(0,0,0,0)",
  plot_bgcolor = "rgba(0,0,0,0)",
  font = list(color = "#000000", size = 12, family = "Arial"),
  margin = list(
    l = 60,
    r = 60,
    b = 60,
    t = 75
  ),
  hoverlabel = list(
    bgcolor = "rgba(255, 255, 255, 1)",
    bordercolor = "rgba(0, 0, 0, 1)",
    font = list(color = "black")
  )
)

fig
```

###### Sankey diagram generated using Plotly in R

---

## Interests and Hobbies
##### Click on the circles to see more!
\
\


```{r}
library(circlepackeR)

data <- data.frame(
  root = rep("root", 15),
  group = c(
    rep("Sports", 3),
    rep("Languages", 3),
    rep("Music", 3),
    rep("Digital Creation", 4),
    rep("Learning", 2)
  ),
  subgroup = rep(c(
    "Calisthenics",
    "Running",
    "Swimming",
    "Arabic",
    "English",
    "Mandarin",
    "Playing Piano",
    "Music Theory",
    "Listening",
    "Vector Art",
    "3D Asset Creation",
    "Animation",
    "Raster Art",
    "Reading",
    "Research"
  )
  ),
  value = c(100, 25, 25, 100, 100, 5, 25, 25, 25, 100, 25, 25, 100, 100, 100)
)

library(data.tree)
data$pathString <- paste(
  "world",
  data$group,
  data$subgroup,
  data$subsubgroup,
  sep = "/"
)
population <- as.Node(data)

p <- circlepackeR(
  population, size = "value",
  color_min = "hsl(0, 0%, 90%)",
  color_max = "hsl(0, 0%, 10%)"
)

p
```
\
\

###### Circle packing generated using circlepackeR in R
